Semantic Authoring in the \sTeX/\ALeA World \ednote{Find better title. Was ``Bulk Semantic Annotation with a Partially Known Knowledge Base'' }

### 2025-01-27 doc/cicm25-sysdesc/sysdesc.tex

\title{Bulk Semantic Annotation with a Partially Known Knowledge Base\ednote{
    Too \snify specific...
}}
\author{Michael Kohlhase, Jan Frederik Schaefer}
\institute{Computer Science, FAU Erlangen N\"urnberg, Germany}
\begin{document}
\maketitle
\begin{abstract}
  Semantic annotations can be utilized for learning support services in technical
  documents. The resulting active documents support more direct and personalized
  interaction with the knowledge conveyed, but require a large investment in the authoring
  process.

@@

\paragraph{Overview}
We argue that semantic/flexiformal authoring shares aspects with both informal and fully formal authoring,
but is nevertheless a distinct problem requiring special tool support (\cref{sec:semauth}).
Afterwards, we discuss (potential) tools in various stages of development (\cref{sec:tools}) and then
describe and evaluate one concrete tool, \snify, that supports the annotation
of terms with the semantic concepts they refer to (\cref{sec:snify,sec:eval}).
The paper ends with a brief conclusion (\cref{sec:conclusion}).
\ednote{rework this paragraph a bit -- make it contribution and overview at the same time?}

>>>>

\title{
    Semantic Authoring in the \sTeX/\ALeA World
    \ednote{Find better title. Was ``Bulk Semantic Annotation with a Partially Known Knowledge Base''
}}
\author{Michael Kohlhase, Jan Frederik Schaefer}
\institute{Computer Science, FAU Erlangen N\"urnberg, Germany}
\begin{document}
\maketitle
\begin{abstract}
  Semantic annotations can be utilized for learning support services in technical
  documents. The resulting active documents support more direct and personalized
  interaction with the knowledge conveyed, but require a large investment in the authoring
  process.

@@

% \paragraph{Overview \& Contribution}
In this paper, we argue that semantic/flexiformal authoring shares aspects with both informal and fully formal authoring,
but is nevertheless a distinct problem requiring special tool support (\cref{sec:semauth}).
Using \sTeX/\ALeA as an exemplary case study,
we will provide an overview of the authoring support (\cref{sec:tools})
and then describe and evaluate one new, concrete tool, \snify, that supports the annotation
of terms with the semantic concepts they refer to (\cref{sec:snify,sec:eval}).
The paper ends with a brief conclusion (\cref{sec:conclusion}).
